\documentclass[11pt,letterpaper]{article}

% --- PACKAGES ---
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry} 
\usepackage[hidelinks]{hyperref} 
\usepackage{enumitem}
\usepackage{titlesec}

% --- CUSTOM FORMATTING ---
\setcounter{secnumdepth}{0} % Disable section numbering
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}

\pagestyle{empty}

\setlength{\parskip}{0.8em}
\setlength{\parindent}{0pt}

\begin{document}

% --- HEADER ---
\begin{center}
    {\LARGE \textbf{Kushal Sharma}} \\ 
    \vspace{2pt}
    skushal746@gmail.com | \href{https://www.linkedin.com/in/skushal746}{www.linkedin.com/in/skushal746} | \href{https://github.com/skushal746}{https://github.com/skushal746} | 8767716841
\end{center}

\vspace{1.5em}

{\Large \textbf{Proposal -- Backend Developer}} \\
\vspace{0.5em}

Hello,

I'm a Senior Backend Engineer specializing in Java, Spring Boot, and scalable microservices, with experience building production systems for U.S. and India-based companies. I focus on clean architecture, reliable APIs, and performance at scale, which aligns well with your need for someone who can build clean, scalable, and reliable backend systems.

Over the last several years, I have:

\begin{itemize}[leftmargin=0.25in, noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt]
    \item Designed and deployed RESTful APIs and distributed backend services using Java 17/21, Spring Boot, Hibernate, and MySQL/PostgreSQL on AWS, improving system performance and reliability for enterprise clients.
    \item Built microservices architectures with asynchronous messaging (RabbitMQ, schedulers, Spring Batch) to handle cross-device synchronization, background processing, and high-throughput workloads with strong uptime guarantees.
    \item Implemented robust security using Spring Security with OAuth2/JWT, and followed best practices for authentication, authorization, and data protection across multiple applications.
    \item Optimized database access using relational databases and MongoDB, including aggregation pipelines, indexing, and caching (LRU, Redis) to reduce latency and improve throughput.
    \item Maintained high code quality through TDD with JUnit and Mockito, CI/CD pipelines with Maven/Jenkins, and close collaboration with cross-functional teams (frontend, data, product).
\end{itemize}

\section{Representative backend work}

\textbf{1. Enterprise SaaS backend for a U.S.-based client}
\begin{itemize}[leftmargin=0.25in, noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt]
    \item \textbf{Role:} Backend Engineer (Java/Spring Boot).
    \item Built and scaled RESTful APIs and microservices using Java 17/21, Spring Boot, Hibernate, MySQL, and AWS, including ML/NLP-powered search and recommendation features to improve user engagement and query relevance.
    \item Designed distributed schedulers and background jobs with Spring Batch and messaging to ensure high reliability and 99.9\%+ uptime for enterprise customers.
\end{itemize}
\vspace{4pt}

\textbf{2. Real-time tracking and analytics system}
\begin{itemize}[leftmargin=0.25in, noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt]
    \item \textbf{Role:} Backend Developer.
    \item Developed a real-time distributed tracking backend using Spring Boot and Spring JPA, integrating with front-end clients and leveraging asynchronous processing and schedulers for cross-device synchronization.
    \item Focused on observability, reliability, and test coverage (TDD with JUnit/Mockito) to ensure stable behavior under load.
\end{itemize}
\vspace{4pt}

\textbf{3. High-throughput financial data microservices}
\begin{itemize}[leftmargin=0.25in, noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt]
    \item \textbf{Role:} Backend / Full Stack Engineer.
    \item Architected high-throughput microservices with Java and Spring Boot (including non-blocking I/O with Spring WebFlux) to serve real-time financial data streams.
    \item Optimized persistence with MongoDB aggregation pipelines and in-memory caching, reducing query latency and improving responsiveness for demanding clients.
\end{itemize}

\section{How I can help on this project}

For your Backend Developer role, I can:

\begin{itemize}[leftmargin=0.25in, noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt]
    \item Design or refine a scalable backend architecture (service boundaries, data models, and API contracts) suited to your current and future requirements.
    \item Implement clean, well-tested RESTful APIs and supporting services with Java/Spring Boot, focusing on reliability, observability, and maintainability.
    \item Work with relational or NoSQL databases to model data effectively, tune performance, and plan safe migrations as the product evolves.
    \item Integrate third-party services and internal systems while keeping boundaries clean and failure modes well-handled.
    \item Help set up or improve CI/CD, testing, and monitoring so that changes can be shipped confidently.
\end{itemize}

I'd be happy to discuss your current backend setup, immediate priorities, and roadmap, and share how I can help you improve performance, reliability, and developer productivity over the next few months.

Thank you for your time and consideration.

Best regards, \\
\vspace{1em}
Kushal Sharma

\end{document}
