\documentclass[11pt,letterpaper]{article}

% --- PACKAGES ---
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry} 
\usepackage[hidelinks]{hyperref} 

% --- CUSTOM FORMATTING ---
\pagestyle{empty}

\setlength{\parskip}{1em}
\setlength{\parindent}{0pt}

\begin{document}

% --- HEADER ---
\begin{center}
    {\LARGE \textbf{Kushal Sharma}} \\ 
    \vspace{2pt}
    skushal746@gmail.com | \href{https://www.linkedin.com/in/skushal746}{www.linkedin.com/in/skushal746} | \href{https://github.com/skushal746}{https://github.com/skushal746} | 8767716841
\end{center}

\vspace{1.5em}

Dear Hiring Team,

I am excited to apply for the Senior Software Engineer. With over seven years of experience designing and scaling full-stack and distributed backend systems, along with deep proficiency across Java, Spring Boot, JavaScript/TypeScript, React, SQL/NoSQL databases, and cloud-native architectures, I am motivated by the opportunity to contribute to a platform that impacts millions of customers seeking financial empowerment.

At Remora, I have architected scalable REST APIs and backend services, optimized database performance, and developed React-based features that improved user workflows and system reliability by over 30\%. I also built server-side automation pipelines, scheduled tasks, and fault-tolerant components that operate with 99.9\% reliability. This end-to-end ownership—from planning and design to testing, deployment, and monitoring—has shaped my approach to building clean, reusable, and maintainable codebases.

During my time at Sonos, I developed distributed Java applications (Spring Boot, JPA) and frontend components using React, following TDD principles with JUnit and Mockito to deliver resilient, high-quality services. I worked extensively with authentication flows, asynchronous programming, and distributed data pipelines, strengthening my ability to build scalable, observable systems and debug complex issues across service boundaries.

Earlier in my career at Verdantis and QualityKiosk, I engineered microservices and data-heavy systems using Java, Spring, MongoDB, MySQL, ElasticSearch, and AWS. I focused on high-performance API design, caching strategies, search optimization, and containerized deployment patterns—experience that aligns strongly with Toyota's goals of building robust, cloud-based, micro service driven platforms on AWS.

What excites me most about this opportunity commitment to innovation, quality, and respect for people. I am especially drawn to the culture of continuous improvement, cross-team collaboration, learning, and operational excellence, values that closely mirror my own.

With strong full-stack expertise, a track record of building scalable distributed services, and a passion for delivering high-quality financial technology solutions. Thank you for considering my application.

Sincerely, 

\vspace{1em}
Kushal Sharma

\end{document}
